Effects of Trauma Life Support Training Programs on Patient Outcomes: A Pilot Cluster Randomised Trial

### 2024-10-04 pilot-publication/manuscript.Rmd
Add flowchart to manuscript
Try to compile revised manuscript, work on table errors

```{r flow-diagram, echo = FALSE, fig.cap="Study flow diagram. Abbreviations: ATLS, Advanced Trauma Life Support; PTC, Primary Trauma Care."}
create_flow_diagram()
knitr::include_graphics("flow-diagram.png")
```

@@

<!--Out of X potentially eligible patients, X (X%) patients were enrolled
in the study-->. The percentage of patients who consented to follow up was `r p.consent`% and the percentage of residents who consented to training was `r recruitment.rate.residents`%. The lost to follow up rate was `r rate.lost.to.follow.up`%. The pass rate was `r pass.rate`%. The missing data rate ranged from `r min.missing.data` to `r max.missing.data`, with details for selected variables shown in Table \ref@(tab:sample-characteristics). The differences in distributions between observed data and data extracted from medical records, for selected variables that were collected through observation or interview, are shown in Table \ref@(tab:observed-vs-retrospective). Overall, the data were similarly distributed, but there were considerably more missing values in extracted data compared to observed data.

```{r observed-vs-retrospective, echo = FALSE}
observed.vs.extracted.comparison.table %>%
  modify_caption("Differences in distributions between directly observed data and data extracted from medical records, for selected variables that were collected through observation or interview.")
```

After training, a total of `r m30d.standard.care` patients in the standard care arm died within 30 days, compared to `r m30d.atls` patients in the ATLS^®^ arm and `r m30d.ptc` patients in the PTC arm. The corresponding figures for in-hospital mortality were `r inhosp.standard.care`%, `r inhosp.atls`%, and `r inhosp.ptc`%. Absolute and relative changes from baseline, as well as absolute and relative risk differences, are shown in Table \@ref(tab:outcomes). Overall, both in-hospital and 30-day mortality were substantially lower in the ATLS^®^ and PTC arms compared to the standard care arm, but the absolute numbers of deaths in the ATLS and PTC arms were very small. The results for all other outcomes are shown in Supplementary Materials.

```{r outcomes, echo = FALSE}
outcomes.table.with.differences
```

@@

We conclude that a full-scale cluster randomised trial should be feasible after incorporating the lessons of this pilot.

>>>>

```{r flow-diagram, echo = FALSE, fig.cap="Study flow diagram. Abbreviations: ATLS, Advanced Trauma Life Support; PTC, Primary Trauma Care.", out.width="50%"}
knitr::include_graphics("consort-flow-diagram.png")
```

@@

The percentage of patients who consented to follow up was `r p.consent`% and the percentage of residents who consented to training was `r recruitment.rate.residents`%. The lost to follow up rate was `r rate.lost.to.follow.up`%. The pass rate was `r pass.rate`%. The missing data rate ranged from `r min.missing.data` to `r max.missing.data`, with details for selected variables shown in Table \ref@(tab:sample-characteristics). The differences in distributions between observed data and data extracted from medical records, for selected variables that were collected through observation or interview, are shown in Table \ref@(tab:observed-vs-extracted). Overall, the data were similarly distributed, but there were considerably more missing values in extracted data compared to observed data.

```{r observed-vs-extracted, echo = FALSE}
observed.vs.extracted.comparison.table %>%
  modify_caption("Differences in distributions between directly observed data and data extracted from medical records, for selected variables that were collected through observation or interview.")
```

After training, a total of `r m30d.standard.care` patients in the standard care arm died within 30 days, compared to `r m30d.atls` patients in the ATLS^®^ arm and `r m30d.ptc` patients in the PTC arm. The corresponding figures for in-hospital mortality were `r inhosp.standard.care`%, `r inhosp.atls`%, and `r inhosp.ptc`%, as shown in Table \@ref(tab:outcomes). Overall, both in-hospital and 30-day mortality were substantially lower in the ATLS^®^ and PTC arms compared to the standard care arm, but the absolute numbers of deaths in the ATLS and PTC arms were very small. The results for all other outcomes are shown in Supplementary Materials.

```{r outcomes, echo = FALSE}
outcome.table.with.differences
```

@@

We conclude that conducting a full-scale cluster randomised trial should be feasible after incorporating the lessons of this pilot.
